Improving Haskell Theory Exploration

### 2015-11-30 TransferReport/contributions.tex
Added Core translations
Added TODOs

@@

\subsubsection{Algorithm}
\label{sec:algorithm}

>>>>

\iffalse TODO: Much of this discussion reads as a minor implementation solution rather than an overview of the whole method \fi

\iffalse TODO: Don't show the ``pkg:Mod:name'' format here, it will just be confusing. Leave that to the implementation section. \fi

\iffalse TODO: Focus the section more on the problem of identifiers, and how recurrent clustering uses clustering as part of feature extraction to solve this \fi

\iffalse TODO: Maybe present the translation from trees to matrices, to vectors first; leaving the conversion of terms to features until afterwards; similar to how ML4PG uses [foo] to mean ``the feature corresponding to foo, whatever that might be'' \fi

\iffalse TODO: Maybe present recurrent clustering in a ``naive'' way: define the conversion function ``[]'' recursively. Leave the dependency-ordering, etc. for the Algorithm section, as a way of ``building up to'' the result, which avoids the inefficiencies of recursing. \fi

@@

\subsubsection{Algorithm}
\label{sec:algorithm}
\iffalse TODO: the code should go in the implementation section rather than here \fi
\iffalse TODO: give a more abstract presentation, using mathematical notation \fi
\iffalse TODO: maybe focus on the ``interesting cases'', and defer the nitty-gritty of extending the environment, etc. to the implementation section? \fi
\iffalse TODO: Define rose trees \fi
\iffalse TODO: Show an example from earlier, e.g. factorial \fi
\iffalse TODO: Split into three parts: expressions to rose trees of features; rose trees to matrices to vectors; k-means clustering \fi
\iffalse TODO: highlight the recurrent nature of the algorithm \fi
\iffalse TODO: I would probably just restructure:
 - start with the syntax, get to show how, for every line of figure 1, extraction works
 - then transformation to feature vectors
 - then k-means
obviously, they are mutually recursive...
\fi

### 2015-11-30 TransferReport/implementation.tex
Added TODOs

>>>>

\iffalse TODO: How does this section differ from Algorithm in Contributions? \fi
\iffalse TODO: Make this a concrete presentation of the abstract ideas from the Algorithm section, e.g. this is how we get the dependencies (AST plugin, etc.); this is a case-by-case of how we perform feature extraction; this is how we perform k-means (Weka), etc. \fi
